---
title: "Question on Thousand-Year Tornados"
author: "Till Hainbach"
date: "7 11 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What can we say about the probabilities of observing multiple 1,000-year tornadoes in thousand years?

First we have to create random time series of 1000 events. We set the number of obeservation years to 1000 years. For each year, we modelled uniformly distributed strength.
```{r}
# number of datasets
n = 1000

# create events with random strength
t <- replicate(n, runif(1000))
```


Now we have to count all events within one time serie, that are beyond the thousand-year event threshold (meaning the strongest 0.1%).
```{r}
# observed events of certain strength
obsa <- colSums(t >= 0.999)
```


Display the result in a barplot
```{r}
# plot
barplot(prop.table(table(obsa)), ylab = "probability",
        xlab = "number of events", ylim = c(0,0.4),
        main = "Probability of n thousand-year tornados observed within one time serie")
```


